\documentclass[12pt]{book}

\usepackage[margin=1.0in]{geometry}
\usepackage{amsmath,amsthm,amssymb,titling}

\newcommand{\rr}{\mathbb{R}}
\newcommand{\cc}{\mathbb{C}}
\newcommand{\nn}{\mathbb{N}}
\newcommand{\zz}{\mathbb{Z}}

\newcommand{\subtitle}[1]{%
	\posttitle{%
		\par\end{center}
	\begin{center}\large#1\end{center}
	\vskip0.5em}%
}

\title{Topology Preliminary Exam Study Guide}
\subtitle{NDSU}
\author{James (Jimmy) Thorne}
\date{\today}

\theoremstyle{definition}
\newtheorem{define}{Definition}
\newtheorem{ex}{Exercise}


\begin{document}
	\maketitle
	
	\chapter{Point-Set Topology}
	Since Point-Set Topology is a prerequisite, this section will strictly be
	problems that provide utility to solve problems in Algebraic and Differential
	topology.
	\begin{ex}
		If $f:X\to Y$ is continuous and $Y$ is both compact and Hausdorff, then the
		graph
		
		$$G = \{ (x,y) \in X\times Y | y=f(x) \}$$
		is closed in $X\times Y$.
	\end{ex}

	\begin{ex}
		Let $f:X\to Y$ be a continuous bijection.  If $X$ is compact and $Y$ is 
		Hausdorff, then $f$ is a homeomorphism.
	\end{ex}

	\begin{ex}[Spring 19]
		Give an example of a space that is connected, but not locally path
		connected.  Give an example of a topological space that is  locally
		path connected but not locally simply connected
	\end{ex}

	\begin{ex}[Spring 18]
		 Let $X$ be a Hausdorff topological space.  Show that there exists a compact topological space $Y$ such that $X$ is a subspace of Y and $Y\backslash X$ consists of a single point.
	\end{ex}
	
	\begin{ex}[Spring 18]
		For distinct positive integers $m$ and $n$, prove that $R^m$ is not homeomorphic to $R^n$.
	\end{ex}

	\begin{ex}[Fall 17]
		A  topological  space $X$ is  called locally  Euclidean if for  some
		  fixed $n\leq 1$  and  for  all $p\in X$ there  exists  an  open
		   set $U$ containing $p$ such  that $U$ is  homeomorphic  to $R^n$.   Is
		   it  true  that  a locally Euclidean second countable space is Hausdorff?
	\end{ex}

	\begin{ex}[Fall 17]
		Let $X$ be  a  Hausdorff  topological  space  and $U$ an open subset of $X$.
		Show that if $\{K_n | n\in \nn \}$ is a nested sequence of compact subsets
		of $X$ with $\displaystyle\bigcap_{n=1}^{\infty}K_n\subset U$, then there
		 exists $n \in \nn $ such that $K_n\subset U$.
	\end{ex}

	\begin{ex}[Spring 17]
		Let $X$ be a Hausdorff topological space and let $F,K\subset X$ be disjoint
		 compact subsets.  Show that there exist open sets $U,V\subset X$ such
		  that $F\subset U,K\subset V$ and $U\cap V=\emptyset$.
	\end{ex}

	\begin{ex}[Spring 16]
		Prove the following.(a)  A closed subset of a compact topological space is compact.(b)  A compact subset of a Hausdorff topological space is closed.
	\end{ex}

	\begin{ex}[June 14]
		Find an example of a topological space which is of class a)T0 but not T1. b)T 1but not T2. c)T2 but not T3. d)T3 but not T4.
	\end{ex}
	\chapter{Algebraic Topology}
	\chapter{Differential Topology}
\end{document}